Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-20 Manuscript/manuscript.Rmd
manuscript edits

We evaluated and compared multilpe random forest classification algorithms built of domain data extracted from Hi-C datasets at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}. For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques C = {None, RUS, ROS, SMOTE, ROSE}. A system produced from the ensemble framework was defined as: E = {r, p, v, c}, where r $\in$ R, p $\in$ P, v $\in$ V, and c $\in$ C. Letting |X| denote the cardinality of each set, we evaluated |R| x |P| x |V| x |C| different ensemble systems, totaling 120 (=4 $\times$ 3 $\times$ 2 $\times$ 5) separate models. For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.

We created an ensemble framework to systematically evaluate the performance of of TAD boundary prediction under different conditions and resampling approaches (Figure 3). Briefly, we used Hi-C datasets at four different resolutions $R = \{ 10 kb, 25 kb, 50 kb, 100 kb \}$, used three predictor types $P = \{ OC, OP, Distance \}$, two variable reduction techniques $V = \{ LASSO, Elastic-Net \}$ [??? Is that so?], and five class balancing techniques $C = \{ None, RUS, ROS, SMOTE, ROSE \}$. A system produced from the ensemble framework was defined as: $E = \{ r, p, v, c \}$, where $r \in R$, $p \in P$, $v \in V$, and $c \in C$. Letting $|X|$ denote the cardinality of each set, we evaluated $|R| \times |P| \times |V| \times |C|$ different ensemble systems, totaling $120 (=4 \times 3 \times 2 \times 5)$ [??? Check if you use Lasso only] separate models. For simplicity, we present the most significant results, with the complete results available as Supplementary Tables.

>>>>

We evaluated and compared multilpe random forest classification algorithms built on domain data extracted from Hi-C datasets for X cell lines C = {GM12878, K562, ...}, at four different resolutions R = {10 kb, 25 kb, 50 kb, 100 kb}. For each classifier, we compared 3 predictor types P = {OC, OP, Distance} and 5 class balancing techniques B = {None, RUS, ROS, SMOTE, ROSE}. A system produced from the ensemble framework was defined as: E = {c, r, p, b}, where c $\in$ C, R $\in$ R, p $\in$ P, and b $\in$ B. Letting |X| denote the cardinality of each set, we evaluated |C| x |R| x |P| x |B| different ensemble systems, totaling X (=x $\times$ 4 $\times$ 3 $\times$ 5) separate models. For simplicity, we present the most significant results, with the complete results available as Supplementary Tables and Figures.
